A template for the \emph{arxiv} style

### 2022-09-16 paper-rmd/ptn_platediagram.tex
paper edits
created revised manuscript

\begin{tikzpicture}

@@

     % Plates
     {
       \tikzset{plate caption/.append style={below=15pt of #1.south east}};
       \tikzstyle{plateIJK} = [align=center];
       \plate[inner sep=0.25cm, xshift=-.0625cm] {plateIJK} {(mu)(y)} {$ijk$} ;
    }
     {
       \tikzset{plate caption/.append style={above right=0pt of #1.north east}};
       \plate[inner sep=0.25cm, xshift=-.12cm, yshift=-.12cm] {plateJ} {(mu)(y)(p)(d)(d_prime)(delta)(delta_delta)} {$j$} ;
     }
     {
       \tikzset{plate caption/.append style={above right=0pt and 0pt of #1.north west}};
       \plate[inner sep=0.25cm] {plateIJ} {(p)(mu)(y)} {$jk$};
     }

@@

   \end{tikzpicture}

>>>>

\begin{figure}
  \begin{minipage}{.5\textwidth}
    \flushright
    \begin{tikzpicture}

@@

     % Plates
     {
       \tikzset{plate caption/.append style={below=15pt of #1.south east}};
       \tikzstyle{plateIJK} = [align=center];
       \plate[inner sep=0.25cm, xshift=-.0625cm] {plateIJK} {(mu)(y)} {$i$} ;
    }
     {
       \tikzset{plate caption/.append style={above right=0pt of #1.north east}};
       \plate[inner sep=0.25cm, xshift=-.12cm, yshift=-.12cm] {plateJ} {(mu)(y)(p)(d)(d_prime)(delta)(delta_delta)} {$j$} ;
     }
     {
       \tikzset{plate caption/.append style={above right=0pt and 0pt of #1.north west}};
       \plate[inner sep=0.25cm] {plateIJ} {(p)(mu)(y)} {$k$};
     }

@@

\end{tikzpicture}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \flushleft
    \small
    \begin{align*}
      y_{ijk} &\sim Beta\big(\mu_{ijk} \kappa, (1-\mu_{ijk}) \kappa \big) \\
      \mu_{ijk} &= f_{PT+N}(\overrightarrow{p_{jk}}, d_j, d_j)  \\
      d_j &= \frac{1}{2} \ \text{logistic}(\delta_j) \\
      d_j’ &= \frac{1}{2} \ \text{logistic}\big(\delta_j + \exp(\Delta\delta_j)\big) \\
      \overrightarrow{p_{jk}} &\sim Dirichlet(\overrightarrow{1}) \\
      \delta_j &\sim Normal(0,1) \\
      \Delta\delta_j &\sim Normal(0,1) \\
      \kappa &\sim \mathit{Half \hyph Cauchy}(20)
    \end{align*}
  \end{minipage}
  \caption{Complex unpooled PT+N model diagram and formula specifications. Circular nodes are parameters, shaded nodes are observations, and squared nodes are deterministic functions of parameters. Plates signify values defined for $i$ trials, $j$ participants, and $k$ conditions.}
\end{figure}
